Arc Blanc: a real time ocean simulation framework

### 2024-11-14 paper.tex
Fix images size and plural

Finally, \framework uses a last parameter $\delta\in[0,1]$ that represents how much the waves orientation is constant ($\delta = 0$) or not ($\delta = 1$) (see Figure \ref{fig:dispersionEffect}).
Its meaning is as follows:
\begin{itemize}
	\item $\delta = 0$ indicates a \emph{neutral} directional spectrum, that has no consequence on $\tilde{h}_0$;
	\item $\delta=1$ indicates a spectrum equals to $D_{DB\xi}(\omega, \theta)$.
\end{itemize}
This gives the final expression of the custom Donelan-Banner spectrum used in \framework:
\begin{equation}
	D(\omega, \theta)=\left(1-\delta\right)\frac{1}{2\pi}+\delta D_{DB\xi}(\omega,\theta).
\end{equation}

@@

	\subfloat[Using $\delta = 0$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/seaDispersion0SeaState5-contrast.png}
		\label{fig:dispersion0}
	}
	\hspace{1cm}
	\subfloat[Using $\delta = 1$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/seaDispersion1SeaState5-contrast.png}
		\label{fig:dispersion1}
	}
	\caption{Effect of the dispersion parameter on sea state $5$ on the Beaufort scale.}
	\label{fig:dispersionEffect}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cascades}
\label{subsec:cascades}
While the expression of the water height in Equation \ref{equa:heightWater} is convenient, it may result in an ocean surface that appears overly repetitive.
A naive solution to handle this problem consists in using a huge resolution $N$, but it has a major impact on performance.
\Framework uses the more efficient solution proposed by Dupuy and Bruneton (2012) \cite{dupuyRealtimeAnimationRendering2012}.
It consists in dividing the spectrum into $c$ layers or \emph{cascades} of different length.
Each of these layers represents a different wavelength in Equation~\ref{equa:heightWater}.
The length of the $i$-th cascade is denoted by $L_i$.
These lengths $L_i$ are parameters in the expression of the wave vector component described in Equation~\ref{equa:heightWater}.
Moreover, the different cascades are cut off at arbitrary value to avoid overlap between them, as illustrated in Figure~\ref{fig:cascades}.

>>>>

Finally, \framework uses a last parameter $\delta\in[0,1]$ that represents how much the waves orientation is constant ($\delta = 0$) or not ($\delta = 1$) (see Figure~\ref{fig:dispersionEffect}).
Its meaning is as follows:
\begin{itemize}
	\item $\delta = 0$ indicates a \emph{neutral} directional spectrum, that has no consequence on $\tilde{h}_0$;
	\item $\delta=1$ indicates a spectrum equals to $D_{DB\xi}(\omega, \theta)$.
\end{itemize}
This gives the final expression of the custom Donelan-Banner spectrum used in \framework:
\begin{equation}
	D(\omega, \theta)=\left(1-\delta\right)\frac{1}{2\pi}+\delta D_{DB\xi}(\omega,\theta).
\end{equation}

@@

	\subfloat[Using $\delta = 0$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion0SeaState5-contrast.png}
		\label{fig:dispersion0}
	}
	\hfill
	\subfloat[Using $\delta = 1$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion1SeaState5-contrast.png}
		\label{fig:dispersion1}
	}
	\caption{Effect of the dispersion parameter on sea state $5$ on the Beaufort scale.}
	\label{fig:dispersionEffect}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cascades}
\label{subsec:cascades}
While the expression of the water height in Equation \ref{equa:heightWater} is convenient, it may result in an ocean surface that appears overly repetitive.
A naive solution to handle this problem consists in using a huge resolution $N$, but it has a major impact on performance.
\Framework uses the more efficient solution proposed by Dupuy and Bruneton (2012) \cite{dupuyRealtimeAnimationRendering2012}.
It consists in dividing the spectrum into $c$ layers or \emph{cascades} of different lengths.
Each of these layers represents a different wavelength in Equation~\ref{equa:heightWater}.
The length of the $i$-th cascade is denoted by $L_i$.
These lengths $L_i$ are parameters in the expression of the wave vector component described in Equation~\ref{equa:heightWater}.
Moreover, the different cascades are cut off at arbitrary value to avoid overlap between them, as illustrated in Figure~\ref{fig:cascades}.
